Constraining tensorial and scalar couplings with $B\to K\bar\mu\mu$ and $B_s\to \bar\mu\mu$

### 2015-04-02 tensor/draft/draft-tensor-op.tex
[tensor/draft] use new plots

%--------+---------+---------+---------+---------+---------+---------+---------+
%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+

@@

\begin{figure*}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/FH-15-22_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-K-15-22_vs_cT.pdf}
\\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_cT.pdf}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+
    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability.
    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9}
    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).}
  }
  \label{fig:FHvsCT}
\end{figure*}

>>>>

%
% useful variable for multiple same-size plots
%
\newlength{\relwidth}
%--------+---------+---------+---------+---------+---------+---------+---------+
%
%
%
%--------+---------+---------+---------+---------+---------+---------+---------+

@@

\begin{figure*}
  \setlength{\relwidth}{0.31\textwidth}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_FH15to22}
  \\
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR1to6}
  \includegraphics[width=\relwidth]{plots/pdf/ct_K_BR15to22}
  \\
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-1-6_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-14-16_vs_cT.pdf}
  \includegraphics[width=.24\textwidth]{plots/pdf/Br-Kstar-16-19_vs_cT.pdf}
  \caption{
    \eos{The sensitivity of $F_H^\mu$ [upper row: 1, 2], ${\cal B}(B^+ \to K^+
    \bar\mu\mu)$ [upper row: 3, 4] and ${\cal B}(B^0 \to K^{*0} \bar\mu\mu)$
    [lower row] integrated over $q^2$ at low and high $q^2$ to the tensorial
    coupling $\wilson{T}$. The bands represent the theory uncertainties at
    68\% probability.
    For comparison two values of $\wilson[NP]{9} = 0$ (red) and $\wilson[NP]{9}
    = -1.3$ (green) are shown together with the 68\% measurements of LHCb (blue).}
  }
  \label{fig:FHvsCT}
\end{figure*}
